### 2025-08-14 docs/Homeownership_BankOfMomAndDad.tex
Close #10

\subsection{MPCs}
If altruism makes illiquid assets more attractive, a natural question is how altruism affects MPCs, as liquidity constraints are an important driver of MPCs \citep[see e.g.,][]{aguiar2024hand,Kaplan2014,fagereng2021mpc}. We begin by computing counterfactual MPCs for households in the stationary distribution, assuming no altruistic transfers. The average MPC of young households is 0.32. The MPC of liquidity constrained households (0.43) is about three times that of unconstrained households (0.14). While these MPCs are lower than empirical estimates---typically ranging from 0.5 to 0.9---they are relatively standard in models not designed to generate high MPCs.

>>>>

\subsection{MPCs}
If altruism makes illiquid assets more attractive, a natural question is how altruism affects MPCs, as liquidity constraints are an important driver of MPCs \citep[see e.g.,][]{aguiar2024hand,Kaplan2014,fagereng2021mpc}. We begin by computing counterfactual MPCs for households in the stationary distribution, assuming no altruistic transfers. The average MPC of young households is 0.32. The MPC of liquidity constrained households (0.43) is about three times that of unconstrained households (0.14). While these MPCs are lower than empirical estimates---typically ranging from 0.3 to 0.9---they are relatively standard in models not designed to generate high MPCs.
